---
title: Histograms
author: Sara Conklin
date: '2017-10-06'
slug: histograms
categories: []
tags: []
---

## Step 1: Bring in Packages

In order to start the process, we must first obtain the Lahman, sqldf, and ggplot2 packages. Once obtained, we must bring the packages through 'library'. We do this as follows: 

```{r}
library(Lahman)
library(sqldf)
library(ggplot2)

```


## Step 2: Extract the Data 

We can now begin assembling our Histogram. For this to work, we have to first extract the desired data. For instance, say we wished to know the body-weight distribution for baseball players. We would write that as follows: 

```{r}
query<-"SELECT weight 
FROM Master"

result<-sqldf(query)

```


## Step 3: Visualize the Data

We are now ready to visualize the data in the form of a histogram. We must use the gglot2 package, primarily. In order to let the package know what kind of graph we would like to use, we would write 'geom_histogram'. Notice that we can dictate what we wish the x and y titles to be. We can also change the bin number in order to see our information more clearly. If we so wish, we can also change the color of the inside and of the outline of our bins. Let's take a look: 

```{r}
ggplot()+
  geom_histogram(data=result,aes(x=weight),color="blue", fill="white",bins=50)+
  ggtitle("Body-Weight Distibution for Baseball Players")
```

