---
title: Scatterplots
author: Sara Conklin
date: '2017-10-06'
slug: scatterplots
categories:
  - R Script
tags: []
---

```{r}
library(Lahman)
library(sqldf)
library(ggplot2)

```

## Step 1: Extracte the Data

In order to begin, we must first extracte the data. We must do this and store the data in 'result' in order to link your scatterplot to the data you extracted.For instance, we might want to find the players who have career homeruns greater or equal to 400. We would write that like this: 

```{r}
query<-"SELECT playerID,sum(HR) AS career_HR ,sum(SO) AS career_SO
FROM Batting
GROUP BY playerID
HAVING sum(HR)>=400"

result<-sqldf(query)
```

## Step 2: Visualize the Data

After we have extracted the data and stored the data in 'result', we can now begin to vizualize said data. In order to do that, we will introduce a new package called ggplot. This package allows us to create differnt kinds of graphs. In this instance, we would like to create a scatterplot graph. We would write: 

```{r}
ggplot()+
  geom_point(data=result,aes(x=career_SO,y=career_HR), size=3, color="blue")+
  ggtitle("Career Strikeouts vs Homeruns for Great Hitters")+
  xlab("Career Strikeouts")+
  ylab("Career Homeruns")
```


