---
title: Scatterplots
author: Sara Conklin
date: '2017-10-06'
slug: scatterplots
categories:
  - R Script
tags: []
---

```{r}
library(Lahman)
library(sqldf)
library(ggplot2)

```

## Step 1: Extract the Data

In order to begin, we must fist bring into our Rmarkdown page the packages Lahman, sqldf, and ggplot2. We bring these in by using 'library' as shown above. We are then ready to extract our chosen data. We must do this and store the data in 'result' in order to link our scatterplot to the data we extracted.For instance, we might want to find the players who have career homeruns greater or equal to 400. We would write that like this: 

```{r}
query<-"SELECT playerID,sum(HR) AS career_HR ,sum(SO) AS career_SO
FROM Batting
GROUP BY playerID
HAVING sum(HR)>=400"

result<-sqldf(query)
```

## Step 2: Visualize the Data

After we have extracted the data and stored the data in 'result', we can now begin to vizualize said data. In order to do that, we will introduce a new package called ggplot. This package allows us to create differnt kinds of graphs. In this instance, we would like to create a scatterplot graph. We would write: 

```{r}
ggplot()+
  geom_point(data=result,aes(x=career_SO,y=career_HR), size=3, color="blue")+
  ggtitle("Career Strikeouts vs Homeruns for Great Hitters")+
  xlab("Career Strikeouts")+
  ylab("Career Homeruns")
```


